Supporting Information for ``Seniority and hierarchy configuration interaction for radicals and excited states''

### 2023-07-18 Manuscript/sup.tex
saving work

%%% FIG S2 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes_rpt2}
\caption{
Potential energy curves for \ce{OH}, \ce{CN}, vinyl, and \ce{H7},
according to hCI (green), excitation-based CI (red) and sCI (blue) models
corrected with second-order Epstein-Nesbet perturbative correction.
}
\label{fig:plot_pes_rpt2}
\end{figure*}
%%% %%% %%%

%%% FIG S3 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes_closed}
\caption{
Potential energy curves for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
according to hCI (green), excitation-based CI (red) and sCI (blue) models.
Results first reported in Ref. \onlinecite{Kossoski_2022}.
}
\label{fig:plot_pes_closed}
\end{figure*}
%%% %%% %%%

%%% FIG S4 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes_closed_rpt2}
\caption{
Potential energy curves for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
according to hCI (green), excitation-based CI (red) and sCI (blue) models
corrected with second-order Epstein-Nesbet perturbative correction.
}
\label{fig:plot_pes_closed_rpt2}
\end{figure*}
%%% %%% %%%

%%% FIG S5 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_all_rpt2}
\caption{
Non-parallelity errors, distance errors, equilibrium distances, and vibrational frequencies (or force constants), for \ce{OH}, vinyl, and \ce{H7},
as a function of the number of determinants, according to hCI (green), excitation-based CI (red) and sCI (blue) models
corrected with second-order Epstein-Nesbet perturbative correction.
For \ce{CN}, the perturbative correction produces discontinuous potential energy curves due to the change of character of the unperturbed ground state, as explained in the main text.
}
\label{fig:plot_all_rpt2}
\end{figure*}
%%% %%% %%%

%%% FIG S6 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_all_closed}
\caption{
Non-parallelity errors, distance errors, equilibrium distances, and vibrational frequencies (or force constants), for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
as a function of the number of determinants, according to hCI (green), excitation-based CI (red) and sCI (blue) models.
Results first reported in Ref. \onlinecite{Kossoski_2022}.
}
\label{fig:plot_all_closed}
\end{figure*}
%%% %%% %%%

%%% FIG S7 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_all_closed_rpt2}
\caption{
Non-parallelity errors, distance errors, equilibrium distances, and vibrational frequencies (or force constants), for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
as a function of the number of determinants, according to hCI (green), excitation-based CI (red) and sCI (blue) models,
corrected with second-order Epstein-Nesbet perturbative correction.
}
\label{fig:plot_all_closed_rpt2}
\end{figure*}
%%% %%% %%%

>>>>

%%% FIG S3 %%%
\begin{figure*}%[h!]
\includegraphics[width=1.0\linewidth]{plot_pes_closed}
\caption{
Potential energy curves for \ce{HF}, \ce{F2}, \ce{N2}, ethylene, \ce{H4}, and \ce{H8},
according to hCI (green), excitation-based CI (red) and sCI (blue) models,
with (light tones) and without (dark tones) the EN2 perturbative correction.
Results first reported in Ref. \onlinecite{Kossoski_2022}.
}
\label{fig:plot_pes_closed}
\end{figure*}
%%% %%% %%%
